---
title: "The Good, the Bad, and the Ugly (Charts)"
author: "CM Burch"
date: "2/19/2020"
output: 
  powerpoint_presentation
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
library(dplyr)
library(ggplot2)
library(gridExtra)
library(ggthemes)
```

# On Visualization

## What Is It?
*Data Visualization* is the graphic display of structured or unstructured data in order to convey information.  

Some examples:
```{r chart-examples}
ex_dist <- ggplot(data = diamonds, 
                  aes(x = price, group = cut, fill = cut)) +
  geom_density(adjust = 1.5, alpha = 0.5) + 
  theme_tufte()

ex_grouped_bar <- diamonds %>%
  ggplot(aes(x = cut)) +
  geom_bar(stat = "count", fill = "lightblue", col = "black") +
  theme_tufte()

ex_line <- data.frame(
  Month = factor(c("Jan", "Feb", "Mar", "Apr", "May", "Jun")),
  Vehicles = c(125, 126, 115, 127, 131, 133)
) %>%
  ggplot(aes(x = Month, y = Vehicles, group = 1)) +
  geom_point(fill = "blue") +
  geom_line(col = "black") +
  theme_tufte


grid.arrange(ex_dist, ex_grouped_bar, 
             ex_line, nrow = 2)
```

## For Example
```{r rock-and-roll}
df <- data.frame(material = c("rock", "roll"),
                 amount = c(1, 1),
                 mid = c(0.5, 1.5))
df %>%
  ggplot(aes(x = "", y = amount, fill = material)) +
  geom_bar(width = 1, stat = "identity", col = "white") +
  geom_text(x = 1, aes(y = mid, label = material),
            col = "white", size = 8) +
  coord_polar(theta = "y", start = pi) +
  theme_void() +
  scale_fill_manual(values = c("#88B8F5", "#49B76E")) +
  guides(fill = FALSE) +
  labs(title = "things on which this city was built",
       caption = "Source: Starship (1985)") +
  theme(plot.title = element_text(size = 18,
                                  face = "bold",
                                  hjust = 0.5, 
                                  vjust = -1),
        plot.caption = element_text(size = 10,
                                    hjust = 1,
                                    vjust = 5))
```



## Why Do We Care About Junk Charts?

## How To Identify Junk Charts

# The Culprits

## The Good

## The Bad

## The Ugly

## Elements of Data Analytic Style
Less is More  
Colors encode data differences  


## Some Common Mistakes and How to Fix Them

### Pie Charts
Pie chart problems  
[Pie chart conventions](https://junkcharts.typepad.com/junk_charts/2020/02/pie-chart-conventions.html)

## 

## Slide with R Output

```{r cars, echo = TRUE}
```

## References

- Fung, Kaiser. (2020)[1]. The Unspoken Rules of Visualisation (and when to break them). DataJournalism. https://datajournalism.com/read/longreads/the-unspoken-rules-of-visualisation-and-when-to-break-them
- Fung, Kaiser. (2020)[2]. Junk Charts: Recycling Chartjunk as Junk Art.
https://junkcharts.typepad.com
- Harris, Robert L. (1999). Information Graphics: A Comprehensive Illustrated Reference. USA: Oxford University Press. ISBN 0-19-513532-6.
- Leek, Jeff. (2014). The Elements of Data Analytic Style: A guide for people who want to analyze data. 
- Tufte, Edward R. (1983). The Visual Display of Quantitative Information. Cheshire, CT: Graphics Press.
- Tufte, Edward R. (2006). Beautiful Evidence. Cheshire, CT: Graphics Press.  ISBN 978-0961392178.
- Wilke, Claus O. (2019). Fundamentals of Data Visualization: A Primer on Making Informative and Compelling Figures. Sebastopol, CA: O'Reilly Media, Inc. ISBN 978-1-492-03108-6